A Survey of Sterile Neutrinos

### 2015-04-14 p3_505/paper/paper3.tex
added .gitignore and half of the MINOS section

yep
\subsection{Current Matt}
experiment
\subsection{Future Matt}
is cool

@@

>>>>

Due to the number of anomalous results to date sterile neutrino searches have become popular research topics at the majority of contemporary neutrino experiments, both those currently running and those in the design and construction phases.
\subsection{Current}
%Matt
\subsubsection{MINOS/MINOS+}
The MINOS (Main Injector Neutrino Oscillation Search) experiment ran from 2005 to 2012 and its upgraded second run, MINOS+, has taking data since September 2013. The MINOS experiment is a long baseline style detector with a neutrino beam source and near detector at Fermilab and a far detector located in northern Minnesota. Though it's primary physics goals lie in the area of neutrino oscillation measurements, MINOS and MINOS+ are now also running sterile neutrino analysis with their data. MINOS detects sterile nutrinos via their disappearence in neutral-current (NC) and

The latest results \cite{MINOS+} are still in preprint but

\subsubsection{T2K}

\subsubsection{Daya Bay}

\subsection{Future}
%Matt
NOVA
MicroBooNE
DUNE (Formerly LBNE)

@@

\bibitem{MINOS+}
  Alexandre B. Sousa~\emph{(for the MINOS and MINOS+ Collaborations)} First MINOS+ Data and New Results from MINOS. arXiv:1502.07715v1 [hep-ex] \url{http://arxiv.org/abs/1502.07715}
